Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-22 Manuscript/manuscript.Rmd
manuscript/todo updates

@@

## IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES

The low baseline AUPRC values, denoted by the dashed lines in the above PR curves, indicate the severity of

After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low. Ideally a manageable dataset will have an imbalance ratio hovering near 1. At their heights, the imbalance ratios were 0.179, 0.152, ... for cell lines GM12878, K562, ... respectively (Figure 4).

>>>>

## LOW IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES

After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low. Ideally a manageable dataset will have an imbalance ratio hovering near 1. At their heights, the imbalance ratios were 0.179, 0.152, ... for cell lines GM12878, K562, ... respectively (Figure 6). The imbalance ratio were lowest for the 10 kb resolution data for both GM12878 and K562.

@@
